An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-07-09 gas-adsorption/rsc-gas-ads-complete.tex
reorder sections a bit, and move figures around a bit

\section{An upper bound on the deliverable capacity of a pure gas in a rigid porous material}\label{sec:upper-bound}
\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{methane-298-rho-mu}
  \caption{The density of bulk methane, the ideal gas, and adsorbed gas in several porous materials at 298\ K as a function of chemical potential (bottom axis) and pressure (top axis). The bulk methane density is from the National Institute of Standards and Technology (NIST)~\cite{nist}. The methane adsorption isotherms in the porous materials are experimental data from Ref.~\cite{mason2014evaluating, furukawa2009storage}.
  }
  \label{fig:density-vs-mu-ch4}
\end{figure}

We now develop a thermodynamic framework that places an upper bound on the deliverable capacity of any pure gas in a rigid porous material.

@@

>>>>

\section{Methods}
\subsection{An upper bound on the deliverable capacity}\label{sec:upper-bound}
We now develop a thermodynamic framework that places an upper bound on the deliverable capacity of any pure gas in a rigid porous material.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{methane-298-rho-mu}
    \caption{The density of bulk methane, the ideal gas, and adsorbed gas in several porous materials at 298\ K as a function of chemical potential (bottom axis) and pressure (top axis). The bulk methane density is from the National Institute of Standards and Technology (NIST)~\cite{nist}. The methane adsorption isotherms in the porous materials are experimental data from Ref.~\cite{mason2014evaluating, furukawa2009storage}.
    }
    \label{fig:density-vs-mu-ch4}
  \end{figure}
